---
title: "V2 Naive Bayes"
output: html_notebook
---
# Overview
#   Step: 1. Read file csv to dataframe
#         2. Make class from ridership and tolerance
#         3. Make input to factor for Naive Bayes model
#         4. Seperate trining and test data set of each cell
#         5. Trianing Naibe bayes model
#         6. Test data with model
#         7. Extract accuracy each cell from test data
#         8. Sum accuracy each cell to overall accuracy cell size
```{r}
#load libraly
source("function.R")
start_time <- Sys.time()
```
#   Step: 1. Read data files to dataframe and pepare data to use
```{r}
cell.size <- c(1500)
print(paste0("Cell size: ",cell.size))
df <- read.file.to.data.frame(cell.size)
```
#   Step: 1. Make class from ridership and tolerance
```{r}
tolelance <- c(20)
print(paste0("tolelance is: ",tolelance))

df$class <- make.class(df$ridership, tolerance)
```
#         3. Make input to factor for Naive Bayes model
```{r}
#for map foctor to number
df$day <- as.factor(df$day)
df$time <- as.factor(df$time)
df$class <- as.factor(df$class)
```
#         4. Seperate trining and test data set of each cell
```{r}
startline.of.test = get.start.line.of.test(df);
endline.of.trainning = startline.of.test - 1;

df.training <- select.trianing(df)  # 3 week
df.test <- select.test(df)  # 1 week
```
#         5.1 Trianing Naive bayes model by separate cell & Test data with model
```{r}
cell <- sort(unique(df.training$cell))
df.accuracy <- data.frame(cell = numeric(0), naive_accuracy = numeric(0),  naive_ma_accuracy = numeric(0))
for(cell.index in 1:length(cell)){
        cell.number = cell[cell.index]
        df.training.cell <- df.training[df.training$cell == cell.number,]
        df.test.cell <- df.test[df.test$cell == cell.number,]
        df.cell <- df[df$cell == cell.number,]
        #for Naive bayes
        df.test.cell$prediction <- naive.bayes.model.prediction(df.training.cell, df.test.cell)
        accuracy.nb <- accuracy.naive.bayes(df.test.cell$prediction, df.test.cell$class)
        table.predic <- table(df.test.cell$prediction, df.test.cell$class)
        
        df.accuracy[cell.index,]$cell = cell.number
        df.accuracy[cell.index,]$naive_accuracy = accuracy.nb
        # plot.graph.train.and.test(df, cell.number, df.test.cell$prediction); 
}
print(paste0("Mean value of all cell NaiveBayes: ",mean(df.accuracy$naive_accuracy, na.rm=TRUE)))
end_time <- Sys.time()
print(paste("Running time", end_time - start_time))
```
#         5.2 Trianing Naive bayes model by make cell number as factor & Test data with model
```{r}
df$cell <- as.factor(df$cell)
df$day <- as.factor(df$day)
df$time <- as.factor(df$time)
df$class <- as.factor(df$class)
df.training <- select.trianing(df)  # 3 week
df.test <- select.test(df)  # 1 week
df.test$prediction <- naive.bayes.model.prediction(df.training, df.test)
accuracy.nb <- accuracy.naive.bayes(df.test$prediction, df.test$class)
print(paste0("Mean value of all cell NaiveBayes: ",accuracy.nb))
```
# 5.2.1 other solution
```{r}
df.all <- df[,c("timeslot","cell","day","time","class")]
df.all$cell <- as.factor(df$cell)
df.all$day <- as.factor(df$day)
df.all$time <- as.factor(df$time)
df.all$class <- as.factor(df$class)
df.training <- select.trianing(df.all)  # 3 week
df.test <- select.test(df.all)  # 1 week
df.test$prediction <- naive.bayes.model.prediction(df.training, df.test)
accuracy.nb <- accuracy.naive.bayes(df.test$prediction, df.test$class)
print(paste0("Mean value of all cell NaiveBayes: ",accuracy.nb))
```

